BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-04-24 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
working on cover letter; but too real, will need to make old jerk curators the heros

Most of the local run time is attributable to the spatial (`r sum(tt_local[tt_local$Module=='Geospatial', 'elapsed'])`sec), and taxonomic operations (`r sum(tt_local[tt_local$Module=='Taxonomic', 'elapsed'])`sec), while formatting data for labels took `r sum(tt_local[tt_local$Module=='Style', 'elapsed'])`sec. 
The spell check of the scientific name accounted for nearly all of the time (`r sum(tt_local[tt_local$Function=='spell_check', 'elapsed'])`sec) spent performing local taxonomic operations.
The generation of labels consumed around `r minutemen(time_label_gen)` minutes (`r time_label_gen`sec) for the rendering, and an additional `r time_final`sec to combine the 182 sheets to a single Portable Document Format (PDF). 
The total label generation run time for processing these `r n_spp` collections was `r minutemen(sum(time_trials$elapsed))` minutes. 
In total the `r n_spp` collections, which underwent all processing steps, took `minutemen(sum(time_trials$elapsed, time_label_gen, as.numeric(time_final)))` minutes to process.

>>>>

Most of the local run time is attributable to the spatial (`r sum(tt_local[tt_local$Module=='Geospatial', 'elapsed'])`sec), and taxonomic operations (`r sum(tt_local[tt_local$Module=='Taxonomic', 'elapsed'])`sec), while formatting data for labels took `r sum(tt_local[tt_local$Module=='Style', 'elapsed'])`sec. 
The spell check of the scientific name accounted for nearly all of the time (`r sum(tt_local[tt_local$Function=='spell_check', 'elapsed'])`sec) spent performing local taxonomic operations.
The generation of labels consumed around `r minutemen(time_label_gen)` minutes (`r time_label_gen`sec) for the rendering, and an additional `r time_final`sec to combine the 182 sheets to a single Portable Document Format (PDF). 
The total label generation run time for processing these `r n_spp` collections was `r minutemen(sum(time_trials$elapsed))` minutes. 
In total the `r n_spp` collections, which underwent all processing steps, took `r minutemen(sum(time_trials$elapsed, time_label_gen, as.numeric(time_final)))` minutes to process.

### 2025-04-24 manuscript/CoverLetter.rmd
working on cover letter; but too real, will need to make old jerk curators the heros

>>>>

While a great variety of software tools and packages exist for interacting with accessioned herbarium data, far fewer are dedicated towards accessioning material. 
And even fewer of these tools are intended for an actual collector to interact with. 
This isn't terribly surprising, as the number of collectors who are not curators has decreased over the last few years, and the barrier to entry for both activities is generally a degree of eccentricity and particularity. 
Unfortunately, the particularity of curators often makes depositing specimens to herbaria a challenging task for collectors, especially those who work on large projects implemented by federal agencies, such as germplasm collection (e.g. Seeds of Success), ecological monitoring (e.g. National Wetland Condition Assessment, and Assess, Inventory, and Monitor), and have to satisfy the particularities of multiple curators simultaneously.

Fortunately, I have been scolded (which on occasion has included some constructive criticism), by about 10 curators over the last decade and built up a wide knowledge of quirks to watch our for. 
As a manager of young botanists for the last handful of years, I have insisted on maintaining a degree of separation between my employees and curators, in hopes that the small glimmer of hope which the youths have isn't extinguished.
